Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-26 analysis/paper/paper.Rmd
Add better descriptor of statistical analysis and Data and code availability statement

For each measurement, e.g. 2015 tiller incidence, 2016 tiller incidence, a  single  MCMC chain was run for 50,000 steps, with the first 5000 discarded as burn in. The remaining samples were thinned by taking every one-hundredth sample, yielding 5000 independent draws from the posterior distribution of the  parameters of the model. Convergence of the chains was assessed using the coda package in R. The priors of the variances and covariances of the random effects in the  model are locally non-informative priors [74].

@@

>>>>

For each measurement, e.g. 2015 tiller incidence, 2016 tiller incidence, a single MCMC chain was run for 55,000 steps, with the first 5000 discarded as burn in. The remaining 50,000 samples were thinned by taking every tenth sample, resulting in 5000 independent draws from the posterior distribution of the parameters of the model.

@@

## Data and Code Availability

All data generated from this project and code used for analysis are available as a research compendium from <https://github.com/openplantpathology/rice_awd_pests> with instructions on how to cite the compendium and use the Docker file to recreate the full analysis and this manuscript [@Sparks2018].
